---
title: "Lab 3"
author: "Dylan Glave"
date: "1/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(jtools)
library(GGally)
library(broom)
```

## Part 1: Binary/binomial Logistic Regression


Exploring Penguin data to make pairs plot. These show multivariate examples of the variables across many different plot types. 

```{r}
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color = species))
```

Create a subset with only Adelie and Chinstrap Penguins
Since Gentoo is a 'factor,' it keeps a third factor level in the df, even though there are 0 abservations. 
```{r}
adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species))
```

I'll make a graph of how jsut these two compare. 

```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point(aes(color = sex)) +
  facet_wrap(~species)
```

We saw some general patterns that chistraps were a bit alrger (both x and y.) We'll see how binary logistic regression can decifer this. 

### Binary Logistic Regression 
- body mass
- flipper length
- penguin sex


```{r}
adelie_chinstrap_blr <- glm(species ~ body_mass_g + flipper_length_mm + sex,
                            data = adelie_chinstrap, 
                            family = "binomial")
  


```

Look at the outcomes 

```{r}
adelie_chinstrap_blr

summary(adelie_chinstrap_blr)
```

Mass have a value of -8*10^4. 
Adelie is the reference level, or the O in binary. Since Mass is negative, as mass increases, the P(Chinstrap) goes down. 
Flipper length is positive. So, as flipper length increases, an onbservation has a higher possibility of being a Chinstrap Penguin. 
We want to align the coefficients in the above model, with what we ACTUALLY see in the date

```{r}
ggplot(data = adelie_chinstrap, aes(x = species, y = flipper_length_mm)) +
  geom_jitter(aes(color  = sex))
```

Since it's challenging to understand Log Odds, from the regression. We ask, what are the actual probabilities of being a chinstrap for each of the existing observations in our adelie_chinstrap df

Augment will add on a column with a probability, based on the model, of being a Chinstrap. The base function would give log odds, we'll translate it to P()

```{r}
blr_fitted <- adelie_chinstrap_blr %>% 
  broom::augment(type.predict = "response")


```



```{r}

```

